Accelerated Magnetic Resonance Imaging by Adversarial Neural Network

### 2018-02-05 paper.tex
Update chart + statisticlly significat

In equilibrium, the generator $G$ is able to generate samples that look like the real data. In our case, $G$ estimates the missing k-space samples from a linear combination of the sampled data and a uniform noise with distribution $p_{u}\left(z\right)$. An L2 fidelity constraint is added to the adversarial loss of the generator, as follows:

@@

%\begin{figure}[H]
%	\centering{}\includegraphics[width=7.8cm,height=4cm]{include/grp1/chart}\caption{\label{fig:system} \textcolor{black}{\footnotesize{}{}Framework
%			architecture: $G$ and $D$ are the generator and discriminator networks,
%			respectively. $F$ is a $2D$ IFFT operator.}}
%\end{figure}

\begin{figure}[H]
	\centering{}\includegraphics[width=12.0cm,height=4cm]{include/grp2/system_chart}\caption{\label{fig:system} \textcolor{black}{\footnotesize{}{}Framework
			architecture: $G$ and $D$ are the generator and discriminator networks,
			respectively.}}
\end{figure}

@@

An additional validation of our model is performed by calculating the PSNR measure on different brain tissues. We applied the commonly used FAST~\cite{zhang2001segmentation} image segmentation algorithm, on the original fully-sampled MR image and then used it for calculating the masked-PSNR on gray matter (GM), white matter (WM) and the Cerebrospinal Fluid (CSF). Results are presented in~Table~\ref{tbl:PSNR_WITH_MASK}.

@@

We next used SSIM, which is a full reference metric, and is considered as a perception-based model, to measure the similarity between the original fully-sampled images and the reconstructed ones.
It quantifies the degradation caused by sampling artifacts based on pixels' inter-dependencies in the image. SSIM scores for different sampling factors, for all methods compared, are presented in~Table~\ref{tbl:SSIM_NO_MASK}. The advantage of our method is clearly shown. All pairwise comparisons between the results obtained by our method and the others are statistically significant (p-values~$<0.0001$) for all sampling factors.

@@

\subsection{Brain Segmentation}
We next tested and compared segmentation quality applying brain tissue partitioning algorithm (FAST \cite{zhang2001segmentation}) to the reconstructed images. Segmentation results were compared to those obtained for the original fully-sampled scans. We believe that these comparisons are indicative to the diagnostic quality of the reconstructed MRIs as tissue segmentation (WM, GM and CSF) plays a key role in clinical brain analysis.
%Segmentation compatibility demonstrate the quality of the proposed MRI reconstruction with respect to other methods. We create a reference segmentation by extracting the brain (using BET \cite{smith2002fast}) from the original fully-sampled image and perform a brain segmentation algorithm (FAST \cite{zhang2001segmentation}) on it. Then, we did the same process for all the reconstruction methods and compared the segmentation results.
We used the Dice score~\cite{dice1945measures} to measure the compatibility between the segments obtained for the original ($S_{\mbox{\tiny{REF}}}$) and the reconstructed ($S_{\mbox{\tiny{REC}}}$) images, defined as follows:
\begin{equation}
\begin{array}{c}
DICE(S_{\mbox{\tiny{REF}}}, S_{\mbox{\tiny{REC}}}) = 2\frac{S_{\mbox{\tiny{REF}}} \cap S_{\mbox{\tiny{REC}}}}{S_{\mbox{\tiny{REF}}} + S_{\mbox{\tiny{REC}}}}
\end{array}
\end{equation}
Dice scores are between zero to one where one indicates complete overlap between the tested segments. Therefore, higher dice scores imply higher compatibility between reconstructed and original images.
Dice scores for all tested methods and sampling factors are presented in~Table~\ref{tbl:DICE}. As fore previous tests, our method achieves the best scores for all brain tissues and all sampling factors. {\color{red} Statistical significant values (~~) found for [1,2,3,4].}

>>>>

In equilibrium, the generator $G$ is able to generate samples that look like the true data. In our case, $G$ estimates the missing k-space samples from a linear combination of the sampled data and a uniform noise with distribution $p_{u}\left(z\right)$. An L2 fidelity constraint is added to the adversarial loss of the generator, as follows:

@@

\begin{figure}[H]
	\centering{}\includegraphics[width=12.0cm,height=4.5cm]{include/grp2/system_chart}\caption{\label{fig:system} \textcolor{black}{\footnotesize{}{}Framework
			architecture: $G$ and $D$ are the generator and discriminator networks,
			respectively.}}
\end{figure}

@@

An additional validation of our model is performed by calculating the PSNR measure on different brain tissues. We applied the commonly used FAST~\cite{zhang2001segmentation} image segmentation algorithm, on the original fully-sampled MR image and then used it for calculating the masked-PSNR on gray matter (GM), white matter (WM) and the Cerebrospinal Fluid (CSF). Results are presented in~Table~\ref{tbl:PSNR_WITH_MASK}. 
The differences are statistically significant with p-values~$<0.0005$ for CS-MRI and Zero-filled for sampling factors 2.5 and 4, and also for IM-CNN-L2 with p-values~$<0.0001$ for sampling factor 6.

@@

We next used SSIM, which is a full reference metric, and is considered as a perception-based model, to measure the similarity between the original fully-sampled images and the reconstructed ones.
It quantifies the degradation caused by sampling artifacts based on pixels' inter-dependencies in the image. 
%The SSIM between images $I_{\mbox{\tiny{REF}}}$ and $I_{\mbox{\tiny{REC}}}$ is calculated on a multiples sliding windows with size of $N\times N$ as follows:
%\begin{equation}
%\begin{array}{cc}
%  SSIM(I_{\mbox{\tiny{REF}}},I_{\mbox{\tiny{REC}}}) = \frac{(2\mu_{I_{\mbox{\tiny{REF}}}}\mu_{I_{\mbox{\tiny{REC}}}} + c_1) (2\sigma_{I_{\mbox{\tiny{REF,REC}}}} + c_2)}{(\mu_{I_{\mbox{\tiny{REF}}}}^2 + \mu_{I_{\mbox{\tiny{REC}}}}^2 + c_1) (\sigma_{I_{\mbox{\tiny{REF}}}}^2) + \sigma_{I_{\mbox{\tiny{REC}}}}^2) + c_2} \\
% second = 2\\
% ohad
%\end{array}
%\end{equation}
%Let $\mu_1,\mu_2$ denote the brain boundaries ext
SSIM scores for different sampling factors, for all methods compared, are presented in~Table~\ref{tbl:SSIM_NO_MASK}. The advantage of our method is clearly shown. All pairwise comparisons between the results obtained by our method and the others are statistically significant (p-values~$<0.0001$) for all sampling factors.

@@

\subsection{Brain Segmentation}
We next tested and compared segmentation quality applying brain tissue partitioning algorithm (FAST \cite{zhang2001segmentation}) to the reconstructed images. Segmentation results were compared to those obtained for the original fully-sampled scans. We believe that these comparisons are indicative to the diagnostic quality of the reconstructed MRIs as tissue segmentation (WM, GM and CSF) plays a key role in clinical brain analysis.
%Segmentation compatibility demonstrate the quality of the proposed MRI reconstruction with respect to other methods. We create a reference segmentation by extracting the brain (using BET \cite{smith2002fast}) from the original fully-sampled image and perform a brain segmentation algorithm (FAST \cite{zhang2001segmentation}) on it. Then, we did the same process for all the reconstruction methods and compared the segmentation results.
We used the Dice score~\cite{dice1945measures} to measure the compatibility between the segments obtained for the original ($S_{\mbox{\tiny{REF}}}$) and the reconstructed ($S_{\mbox{\tiny{REC}}}$) images, defined as follows:
\begin{equation}
\begin{array}{c}
DICE(S_{\mbox{\tiny{REF}}}, S_{\mbox{\tiny{REC}}}) = 2\frac{S_{\mbox{\tiny{REF}}} \cap S_{\mbox{\tiny{REC}}}}{S_{\mbox{\tiny{REF}}} + S_{\mbox{\tiny{REC}}}}
\end{array}
\end{equation}
Dice scores are between zero to one where one indicates complete overlap between the tested segments. Therefore, higher dice scores imply higher compatibility between reconstructed and original images.
Dice scores for all tested methods and sampling factors are presented in~Table~\ref{tbl:DICE}. As fore previous tests, our method achieves the best scores for all brain tissues and all sampling factors. Statistical significant values (p-values~$<0.0005$) found for all methods using sampling factor of 2.5. In addition to the CS-MRI and Zero-filled, the differences are statistically significant with p-values~$<0.0001$ for CNN-L2 using sampling factor 4 and for IM-CNN-L2 using sampling factor 6.
